### 2016-08-23 ms/ms.tex
modified discussion
more discussion modification

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading effects. Following \cite{Memmott2004}, we simulate
the extinction of plant species the subsequent extinction cascades of
pollinator species. Because the reproduction of plant species if
facilitated by active restoration efforts, it is unlikely the
extinction of pollinators would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on
them. Plants species were eliminated based on their degree or
abundance, and the number of pollinators that secondarily went extinct
is calculated. The area below the extinction curve is used as a
measure of network robustness \citep{bipartite}.

We also explored how the robustness to cascading effects changed as
community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity is related to the
mean diameter of a graph and to how difficult it is to turn a network
into completely disconnected groups of nodes, or species
\citep{costa2007characterization} --- the larger the algebraic
connectivity, the more robust a network is to cascading effects
(Gaiarsa et al., submitted), and the harder it is to break the
community into isolated groups of species.

%% marilia:
%% I'm not totally sure what this adds to the methods. Since most
%% people reading this paper will not understand what "spectral
%% properties" are (I don't in fact =/ ) it is a bit of a misdirection
%% since we are not interested in it. I think it is enough to point to
%% your paper which is using the Alg Con the way we want to.

%% removed:
% Algebraic connectivity is
% used to describe spectral properties of complex graphs other than
% ecological networks \citep[e.g.,][]{fiedler1973algebraic,
%   costa2007characterization, mohar1991laplacian, de2007old}.

% what's the mean diameter of a graph? Also can we use the
%% term network instead of graph to be mote consistent with the rest
%% of the methods? We use graph a bit in the change point section, but
%% I think it is explained a bit better there?

%% I also removed the e.g.'s because your paper is all we want to
%% cite, and not "for example Gariarsa et al."

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/robustness.pdf}
  \caption{The robustness of networks to species extinction and
    to cascading effects. The robustness to species extinction is measured by
    incrementally removing species by degree, through removing species
    by abundance did not yield qualitatively different results. The robustness of networks to cascading effects is measured as the algebraic connectivity, the second smallest eigenvalue of the Laplacian matrix. Points
    are the value for each site at each year of assembly. The solid
    line indicates the mean slope estimate and the dashed lines are
    the $95\%$ confidence intervals around the estimate.}
  \label{fig:rob}
\end{figure}
\clearpage

@@

Given that several changing points in network organization occured
during assembly, we next explored the species most likely responsible
for the shifts in interaciton patterns. Based on a preferential
attachment-like mechanism, we expect that the most persistent and high
degree species would remain stable in the network core during
assembly, and would thus contribute the least to the changing points
in network organization. Surprisingly however, we encountered the
opposite: the species that were most variable in their network
position and thus contributed most to network reorganizations where
species with the highest degrees (i.e., most generalized) and
persistence. For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
what module (i.e., community), and they were also present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources the intensively managed
agriculture landscape, and thus also most persistent. More persistent
species also have longer phenologies, so they have the opportunity to
visit many different flowers, resulting in a higher degree. Either
way, our result suggests that adaptable species can change their
network position to utilize the most advantageous floral resources
available, which my depend the other pollinator species that are
present and the state of the floral resource. Thus given the
opportunity and ability to use different resources, species will often
change their network positions.

%% node/species turnover  - I am not sure I get these results so there might be some nonsense in the below paragraph...
Given the regional species pool it is possible that specialization migth be constant either because species are not changing through time, or because there is a species turnover, but new species have the same role/posotion as the species there are absent in the following time step. We found that node turover was higher in assembling and non-assembling hedgerows when compared to field margin, but there was no difference between them. Thus, maybe looking just at network level metrics, such as nestedness and modularity, when exploring the temporal assembly of ecological networks might be misleading, given that there is a node turnover happening at the species level.

@@

The changes in network patterns with assembly also increased the
robustness of the networks to cascading perturbations -- providing
further evidence that hedgerows are valuable tool for promoting
species conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
vulnerability of the network to cascading effects, as measured by
algebraic connectivity, is correlated with species richness, the
increase and plant and pollinator richness following restoration is at
least partially responsible for enhancing network robustness to
cascading effects. The relationship between diversity and stability in
networks has been the subject of considerable debate
\citep[e.g.,][]{may1972will, pimm1984complexity,
  montoya2006ecological}. Our results provides one of the few
empirical examples of how restoring species diversity contributes to
enhancing network stability. Through these hedgerows were designed to
promote floral resrouces across the growing season and not
specifically to promote any specific network properties
\citep{menz-2010-4}, the pollinators assembled into resilent
interaction patterns. With prior knowledge of the floral preferences
of pollinators, future restoration efforts may also be able to
incorporate promoting network stability into planning efforts
\citep{mgonigle2016tool}

%% marilia: not totally sure where you are going here. I was thinking
%% it could be expanded into a whole paragraph on the fact that we
%% don't really understand what effects species persistence, and how
%% that is problematic with understanding netwokr robustness. But
%% maybe it is a bit too far removed from the main message of the
%% paper? Maybe something could be added in the last papergraph about
%% needed more mechanistic models?

%  However, the robustness of ecological
% communities to disturbances might depend on the identity of the
% species mostly being affected by the disturbance (REF). For example,
% networks might be more sensible to the disturbance of a generalist
% when compared to a specialist (REF).

@@

% Other interesting result is that even though nestedness increased
% through time, modularity and connectance did not. \cite{Fortuna2010}
% suggest that at low connectance levels, mutualistic networks would
% present high nestedness and high modularity, while at high connectance
% levels networks would present low nestedness and low
% modularity. However, our results show the contrary: early communities
% presented low nestedness, smaller richness, and higher levels of
% modularity and connectance, while more mature communities presented
% higher nestedness, higher richness, and smaller modularity and
% connectance. SO blabla... XX Temporal overlap.

>>>>

\subsection*{Network robustness}
Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness of the network to species loss
and to cascading perturbations. Following \cite{Memmott2004}, we simulate
the extinction of plant species the subsequent extinction cascades of
pollinator species. Because the reproduction of plant species if
facilitated by active restoration efforts, it is unlikely the
extinction of pollinators would affect plant populations in the
hedgerows. However, plants ceasing to bloom, for example in response
to drought, will likely affect the pollinators that depend on
them. Plants species were eliminated based on their degree or
abundance, and the number of pollinators that secondarily went extinct
is calculated. The area below the extinction curve is used as a
measure of network robustness \citep{bipartite}.

We also explored how the robustness to cascading perturbations changed as
community assembled, using algebraic connectivity --- the second
smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., submitted). Algebraic connectivity is related to how difficult it is to turn a network
into completely disconnected groups of nodes, or species
\citep{costa2007characterization} --- the larger the algebraic
connectivity, the more robust a network is to cascading perturbations
(Gaiarsa et al., submitted), and the harder it is to break the
community into isolated groups of species.

@@

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/robustness.pdf}
  \caption{The robustness of networks to species extinction and
    to cascading perturbations. The robustness to species extinction is measured by
    incrementally removing species by degree, through removing species
    by abundance did not yield qualitatively different results. The robustness of networks to cascading perturbations is measured as the algebraic connectivity, the second smallest eigenvalue of the Laplacian matrix. Points
    are the value for each site at each year of assembly. The solid
    line indicates the mean slope estimate and the dashed lines are
    the $95\%$ confidence intervals around the estimate.}
  \label{fig:rob}
\end{figure}
\clearpage

@@

%% marilia: I see where you are going witht he bluthgen reference, but
%% that seemed like something that should be in the intro or
%% methods. Otherwise it is beinging up a new concept we did not
%% previously explain.

Given that several changing points in network organization occured
during assembly, we next explored the species most likely responsible
for the shifts in interaciton patterns. Based on a preferential
attachment-like mechanism, we expect that the most persistent and high
degree species would remain stable in the network core during
assembly, and would thus contribute the least to the changing points
in network organization. Surprisingly however, we encountered the
opposite: the species that were most variable in their network
position and thus contributed most to network reorganizations where
species with the highest degrees (i.e., most generalized) and
persistence. For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus}, \textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- were the only species that changed
what module (i.e., community), and they were also present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentangle
the causal mechanism for why species with those characteristics are so
variable in their network position. Generalized species may be able to
better exploit the limited floral resources in the intensively managed
agriculture landscape, and thus also most persistent. More persistent
species also have longer phenologies, so they have the opportunity to
visit many different flowers, resulting in a higher degree. Either
way, our result suggests that adaptable species can change their
network position to utilize the most advantageous floral resources
available, which my depend on the other pollinator species that are
present and the state of the floral resource. Thus given the
opportunity and ability to use different resources, species will often
change their network positions.

%% node/species turnover  - I am not sure I get these results so there might be some nonsense in the below paragraph...
Given the regional species pool it is possible that specialization moght be constant because species are not changing their interactions through time, and are thus always presenting the same degree. Alternatively, there might be a species turnover, but new species end up interacting with the same species, and thus, present the same degree as the absent species, and the overall specialization of the network does not change as community assembles. Thus, secies turnover probably happens, but new species might present the same role/posotion as the species previous species. We found that node turnover was higher in assembling and non-assembling hedgerows when compared to field margin, but there was no difference between them. Thus, perhaps looking only at network level metrics, such as nestedness and modularity, when exploring the temporal assembly of ecological networks might be misleading, given that we found node turnover happening at the species level.

@@

The changes in network patterns with assembly also increased the
robustness of the networks to cascading perturbations -- providing
further evidence that hedgerows are valuable tool for promoting
species conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
vulnerability of the network to cascading perturbations, as measured by
algebraic connectivity, is correlated with species richness, the
increase and plant and pollinator richness following restoration is at
least partially responsible for enhancing network robustness to
cascading effects. The relationship between diversity and stability in
networks has been the subject of considerable debate
\citep[e.g.,][]{may1972will, pimm1984complexity,
  montoya2006ecological}. Our results provides one of the few
empirical examples of how restoring species diversity contributes to
enhancing network stability. Though these hedgerows were designed to
promote floral resources across the growing season and not
specifically to promote any specific network properties
\citep{menz-2010-4}, the pollinators assembled into resilent
interaction patterns. With prior knowledge of the floral preferences
of pollinators, future restoration efforts may also be able to
incorporate promoting network stability into planning efforts
\citep{mgonigle2016tool}

@@
